Reconciling agriculture, carbon, and biodiversity in a savanna transformation frontier

### 2016-03-01 paper/supplementary_methods.tex
Submitted version 29/2/2016

The agroEcoTradeoff model was designed to identify optimal land use configurations that allow a certain level of agricultural production to be achieved while minimizing associated ecological and economic costs. The model follows the rationale of Koh and Ghazoul \citep{koh_spatially_2010}, which was designed to select areas with promising potential for oil palm production but whose conversion would result in less loss of carbon, avian diversity, and land with high rice production potential. In this case, each unit of land was ranked based on its relative value within each measure. Normalizing these values converted each into an oil palm conversion probability \emph{c} that was conditioned on the individual land value, such that the highest ranking areas were converted until a specified oil palm production target was reached. For example, in the case of carbon conservation being the priority, lands were sequentially selected from the least carbon dense to the most carbon dense, without concern for any other objective. By multiplying the four \emph{c} values together into a joint conversion probability \emph{C}, each land value was given equal weight, achieving a satisfactory tradeoff between the four different land use objectives.

@@

\begin{figure}[ht]
\captionsetup{width=0.95\linewidth, font=small}
    \begin{center}
       \makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{figures/yields.png} }
      \caption{Predicted yield maps for maize (left) and soybean (right), shown in tons ha$^{-1}$, produced by fitting a generalized additive model to DSSAT-predicted yields at 40 points throughout Zambia where weather stations are located.  The GAM-predicted yields where adjusted so that their mean values matched 2050 projected mean yields for Zambia, derived from FAO data. Yields are shown for locations outside of protected areas (GMAs = game management areas; NatParks = national parks). }
      \label{fig:default}
\end{center}
\end{figure}

@@

@@

\begin{figure}[ht]
\captionsetup{width=0.95\linewidth, font=small}
    \begin{center}
       \makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{figures/cost.png} }
      \caption{Cost distance surface for Zambia, showing travel time in hours to the nearest major town. Travel times are shown for locations outside of protected areas (GMAs = game management areas; NatParks = national parks). }
      \label{fig:default}
\end{center}
\end{figure}

%\section*{\large References}
\bibliographystyle{prsb} 
\bibliography{/Users/lestes/Dropbox/publications/full}

>>>>

Our model was designed to identify optimal land use configurations that allow a certain level of agricultural production to be achieved while minimizing associated ecological and economic costs. The model follows the rationale of Koh and Ghazoul \citep{koh_spatially_2010}, which was designed to select areas with promising potential for oil palm production but whose conversion would result in less loss of carbon, avian diversity, and land with high rice production potential. In this case, each unit of land was ranked based on its relative value within each measure. Normalizing these values converted each into an oil palm conversion probability \emph{c} that was conditioned on the individual land value, such that the highest ranking areas were converted until a specified oil palm production target was reached. For example, in the case of carbon conservation being the priority, lands were sequentially selected from the least carbon dense to the most carbon dense, without concern for any other objective. By multiplying the four \emph{c} values together into a joint conversion probability \emph{C}, each land value was given equal weight, achieving a satisfactory tradeoff between the four different land use objectives.

@@

\begin{figure}[ht]
\captionsetup{width=0.95\linewidth, font=small}
    \begin{center}
       \makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{figures/yields.png} }
      \caption{Predicted yield maps for maize (left) and soybean (right), shown in tons ha$^{-1}$, produced by fitting a generalized additive model to DSSAT-predicted yields at 40 points throughout Zambia where weather stations are located.  The GAM-predicted yields where adjusted so that their mean values matched 2050 projected mean yields for Zambia, derived from FAO data. Yields are shown for locations outside of protected areas. }
      \label{fig:default}
\end{center}
\end{figure}

\subsection*{Carbon}

Figure 2 shows the carbon densities (100\% of vegetative and 25\% of soil carbon in the top 1 m) used by the model to calculate total carbon loss upon conversion to cropland.

\begin{figure}[ht]
\captionsetup{width=0.95\linewidth, font=small}
    \begin{center}
       \makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{figures/carbon.png} }
      \caption{The density of carbon loss (in tons ha$^{-1]}$) per grid cell used by the model to calculate total carbon loss when cells are converted to cropland, as shown for locations outside of existing protected areas. }
      \label{fig:default}
\end{center}
\end{figure}

@@

The final biodiversity index map is shown in Figure 2, with 0 being the lowest value areas and 1 the highest.

\begin{figure}[ht]
\captionsetup{width=0.95\linewidth, font=small}
    \begin{center}
       \makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{figures/bd.png} }
      \caption{Biodiversity index values for Zambia, shown for locations outside of existing protected areas (GMAs = game management areas; NatParks = national parks), excluding forest reserves (visible as the darkest green areas on the map). }
      \label{fig:default}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\captionsetup{width=0.95\linewidth, font=small}
    \begin{center}
       \makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{figures/cost.png} }
      \caption{Cost distance surface for Zambia, showing travel time in hours to the nearest major town. Travel times are shown for locations outside of protected areas. }
      \label{fig:default}
\end{center}
\end{figure}

\clearpage
%\section*{\large References}
\bibliographystyle{prsb} 
\bibliography{/Users/lestes/Dropbox/publications/full}

### 2016-03-01 paper/supplementary_results.tex
Submitted version 29/2/2016

\documentclass[a4paper]{article}
\usepackage[affil-it]{authblk}  
%\newcommand{\citetapos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}  % apostrophe's in cites
\def\linenumberfont{\normalfont\small\sffamily}
\usepackage{graphicx}
\usepackage{epstopdf}
% From link below: next two lines allow caption to fill the full figure box, and caption formats to be changed (e.g. font)
% http://tex.stackexchange.com/questions/107350/caption-below-the-figure-and-aligned-with-left-side-of-figure
% http://ctan.mackichan.com/macros/latex/contrib/caption/caption-eng.pdf
\usepackage[left=2.5cm, right=2.5cm, bottom=2cm, top=2cm]{geometry}
\usepackage{caption}
\captionsetup[figure]{slc=off, font=footnotesize}
\captionsetup[table]{margin={4cm, 4cm}, slc=off, font=footnotesize}
\usepackage[numbers,sort,compress]{natbib}

@@

\section*{\large Crop yields}

\begin{figure}[!ht]
       \begin{center}
       \makebox[\textwidth][c]{\includegraphics[width=0.8\textwidth]{figures/ideal_yield2.png}}
        \end{center}
      \caption{The distribution of converted areas when the model is run separately for maize and soybean when 100\% is placed on yield maximization. The map is color-coded according to which crop was allocated to each location (red for maize, blue for soybean, and yellow for the places where both crops were allocated).}
      \label{fig:default}
\end{figure}

\section*{\large References}
\bibliographystyle{prsb} 
\bibliography{/Users/lestes/Dropbox/publications/full}

>>>>

\documentclass[a4paper]{article}
\usepackage[affil-it]{authblk}  
%\newcommand{\citetapos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}  % apostrophe's in cites
\def\linenumberfont{\normalfont\small\sffamily}
\usepackage{graphicx}
\usepackage{epstopdf}
% From link below: next two lines allow caption to fill the full figure box, and caption formats to be changed (e.g. font)
% http://tex.stackexchange.com/questions/107350/caption-below-the-figure-and-aligned-with-left-side-of-figure
% http://ctan.mackichan.com/macros/latex/contrib/caption/caption-eng.pdf
\usepackage[left=2.5cm, right=2.5cm, bottom=2cm, top=2cm]{geometry}
\usepackage{caption}
\captionsetup[figure]{slc=off, font=footnotesize}
\captionsetup[table]{margin={4cm, 4cm}, slc=off, font=footnotesize}
\usepackage[numbers,sort,compress]{natbib}
\usepackage[skip=2pt,font=normalsize]{caption}

@@

\section*{\large Allocation of land between crops}

To compare the degree to which the cropland allocation routine of \emph{agroEcoTradeoff} causes land that is best for maize to be allocated to soybean and vice versa, we ran the model for each crop separately (with 100\% weight on yield maximization) and compared the overlaps between the resulting conversion maps (Figure 1). The two crops were allocated to the same areas in $<$1\% of converted pixels.

\begin{figure}[!ht]
\captionsetup{width=0.95\linewidth, font=small}
       \begin{center}
       \makebox[\textwidth][c]{\includegraphics[width=0.8\textwidth]{figures/ideal_yield3.png}}
        \end{center}
      \caption{The distribution of converted areas when the model is run separately for maize and soybean when 100\% is placed on yield maximization. The map is color-coded according to which crop was allocated to each location (red for maize, blue for soybean, and yellow for the places where both crops were allocated).}
      \label{fig:default}
\end{figure}

\section*{\large Overlaps with farm blocks}

\begin{figure}[!ht]
\captionsetup{width=0.95\linewidth, font=small}
       \begin{center}
       \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{figures/fb_overlaps.png}}
        \end{center}
      \caption{Simulations run under the 100\% weight to yield maximization and the equal weights scenarios (25\% weight to all objectives), showing the areas of overlap with designated farm development blocks. }
      \label{fig:default}
\end{figure}

\clearpage
\section*{\large Weights associated with 5\% cost compromises}

\begin{table}[ht]
\begin{center}
\captionsetup{width=0.85\linewidth, font=small}
\caption{Weights corresponding to the scenarios in which each objective was a) willing to pay 5\% more than its lowest possible cost, and b) the costs for the other three objectives were minimized equitably.}
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Weights}\\
Objective making 5\% compromise & Yield & Carbon & Biodiversity & Transport Cost \\
\hline\hline
Yield & 40 & 10 & 5 & 45 \\
Carbon & 15 & 75 & 0 & 10 \\
Biodiversity & 15 & 5 & 50 & 30 \\
Travel time & 5 & 5 & 0 & 90 \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}

%\section*{\large References}
\bibliographystyle{prsb} 
\bibliography{/Users/lestes/Dropbox/publications/full}
